The evolution of gene expression in the term placenta of viviparous mammals

### 2015-10-21 manuscript/manuscript.Rnw
order species more usefully

@@

@@

<<load.data,echo=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../data/",c("combined_fpkm","gene_trees","housekeeping_genes_superset","placenta_core_transcriptome","placenta_go_results_bp","placenta_go_results_mf")))>>=
for (a in paste0("../data/",c("combined_fpkm","gene_trees",
                              "housekeeping_genes_superset",
                              "placenta_core_transcriptome",
                              "placenta_go_results_bp",
                              "placenta_go_results_mf"
                              ))) {
    load(a)
}
setkey(genes.to.tree,"gene_id")
star.logs[,value:=gsub("%$","",value)]
star.logs.wide <- 
    data.table(dcast(star.logs,species+file~field))
setnames(star.logs.wide,
         "Average input read length",
         "input.read.length")
setnames(star.logs.wide,
         "Number of input reads",
         "input.reads")
setnames(star.logs.wide,
         "Uniquely mapped reads number",
         "unique.map.reads")
@

>>>>

data.matrix.dt <- function(x){
    temp <- data.matrix(as.data.frame(x)[,-1])
    rownames(temp) <- as.data.frame(x)[,1]
    temp
}

@@

species.names <- 
    list(
        "ateles fusciceps"=
            list(sort.order=1,
                 common.name="Spider monkey",
                 scientific.name="Ateles fuciceps"),
        "homo sapiens"=
            list(sort.order=2,
                 common.name="Human",
                 scientific.name="Homo sapiens"),
        "pan paniscus"=
            list(sort.order=3,
                 common.name="Bonobo",
                 scientific.name="Pan paniscus"),
        "mus musculus"=
            list(sort.order=4,
                 common.name="mouse",
                 scientific.name="Mus musculus"),
        "nannospalax galili"=
            list(sort.order=5,
                 name="nannospalax galili",
                 scientific.name="Nannospalax galili"),
        "spalax carmeli"=
            list(sort.order=6,
                 name="spalax carmeli",
                 scientific.name="Spalax carmeli"),
        "bos taurus"=
            list(sort.order=7,
                 name="Cow",
                 scientific.name="Bos taurus"),
        "ovis aries"=
            list(sort.order=8,
                 name="Sheep",
                 scientific.name="Ovis aries"),
        "sus scrofa"=
            list(sort.order=9,
                 name="Boar",
                 scientific.name="Sus scrofa"),
        "equus caballus"=
            list(sort.order=10,
                 name="Horse",
                 scientific.name="Equus caballus"),
        "canis familiaris"=
            list(sort.order=11,
                 name="Dog",
                 scientific.name="Canis familiaris"),
        "loxodonta africana"=
            list(sort.order=12,
                 name="Elephant",
                 scientific.name="Loxodonta africana"),
        "dasypus novemcinctus"=
            list(sort.order=13,
                 name="Nine banded armadillo",
                 scientific.name="Dasypus novemcinctus"),
        "monodelphis domestica"=
            list(sort.order=14,
                 name="Opposum",
                 scientific.name="Monodelphis domestica"))

@@

<<load.data,echo=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../data/",c("combined_fpkm","gene_trees","housekeeping_genes_superset","placenta_core_transcriptome","placenta_go_results_bp","placenta_go_results_mf")))>>=
for (a in paste0("../data/",c("combined_fpkm","gene_trees",
                              "housekeeping_genes_superset",
                              "placenta_core_transcriptome",
                              "placenta_go_results_bp",
                              "placenta_go_results_mf"
                              ))) {
    load(a)
}
combined.fpkm[,species:=factor(species,levels=names(species.names))]
setkey(genes.to.tree,"gene_id")
star.logs[,value:=gsub("%$","",value)]
star.logs.wide <- 
    data.table(dcast(star.logs,species+file~field))
setnames(star.logs.wide,
         "Average input read length",
         "input.read.length")
setnames(star.logs.wide,
         "Number of input reads",
         "input.reads")
setnames(star.logs.wide,
         "Uniquely mapped reads number",
         "unique.map.reads")
@
